Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students

### 2024-02-15 paper/paper.qmd
Final Edits

As noted by Jack and Oster [-@Jack_Oster_2023], it can be seen that the equity impacts are two-fold. First, as shown in @fig-race, schools (and students) of more vulnerable racial backgrounds -- especially, Black and Hispanic -- are less likely to have access to in-person instruction. Second, as shown in @fig-mathscoresrace and @fig-elascoresrace, for such groups, the consequences of a lack of in-person instruction on academic performance are more severe.

>>>>

Looking at @fig-race alongside @fig-mathscoresrace and @fig-elascoresrace provides insights into the impacts of virtual schooling. As noted by Jack and Oster [-@Jack_Oster_2023], it can be seen that the equity impacts are two-fold. First, as shown in @fig-race, schools (and students) of more vulnerable racial backgrounds -- especially, Black and Hispanic -- are less likely to have access to in-person instruction. Second, as shown in @fig-mathscoresrace and @fig-elascoresrace, for such groups, the consequences of a lack of in-person instruction on academic performance are more severe. We can see how the the districts with a higher share of black and Hispanic students had more virtual days, and also had large decrease in their test scores relative to the districts with lower shares. On the other hand, the districts with a high share of white students had less virtual school days, and had a smaller decrease in their pass rates relative to the districts with lower shares.
